Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-29 main.tex
Little things

In this paper we focus on a well-behaved closed subset of
hyperproperties, where the execution traces remain in {\em lockstep}:
the traces execute identical sequences of instructions. While such
lockstep hyperproperties appear restrictive at first, they are still
of practical interest, as they will allow us to give an extensional
characterization of security policies such as taint tracking or stack
safety, which have been traditionally approached
intentionally. Moreover, this setting admits a principled treatment of
well-bracketed classification and declassification. Finally, a
fortunate side-effect is that because of the lockstep nature of the
execution traces, lockstep-hyperproperties are far easier to test than
their more general counterparts.

Our contributions are:
\begin{itemize}
\item We present a mathematical abstraction of a class of properties
  called {\em lockstep hyperproperties}, that allow for intuitive
  characterizations of interesting security policies.
\item We give an extensional characterization of taint tracking as
  lockstep-noninterference.
\item We introduce a novel stack safety property that allows for
  the notion of observability to change dynamically throughout
  execution.
\item We develop a testing framework for testing such
  lockstep-hyperproperties, implemented as a parametric co-processor
  for RISC-V.
\end{itemize}

@@

\begin{itemize}
\item Daniel's tainting paper (and some refs cited there)
\item Nick and Andre's papers (and other micropolicy papers)
\item StkTokens: Skorstengaard, Devriese, Birkedal
\begin{itemize}
\item {https://arxiv.org/pdf/1811.02787.pdf}
\item {https://arxiv.org/pdf/1902.05283.pdf}
\item {http://cs.au.dk/~lask/papers/esop2018.pdf}
\item {https://dl.acm.org/doi/fullHtml/10.1145/3363519}
\end{itemize}

>>>>

In this paper we focus on a well-behaved closed\bcp{???} subset of
hyperproperties, where the execution traces remain in {\em lockstep}:
the traces execute identical sequences of instructions. While such
lockstep hyperproperties appear restrictive at first, they are still
of practical interest, as they will allow us to give an extensional
characterization of security policies such as taint tracking or stack
safety, which have been traditionally approached
intentionally. \bcp{reword, maybe using ``nested'':}Moreover, this setting
admits a principled treatment of
well-bracketed classification and declassification. Finally, a
fortunate side-effect is that because of the lockstep nature of the
execution traces, lockstep-hyperproperties are far easier to test than
their more general counterparts.

Our contributions are:
\begin{itemize}
\item We present a mathematical abstraction of a class of properties
  called {\em lockstep hyperproperties}, that allow for intuitive
  characterizations of interesting security policies.
\item We give a novel {\em extensional} characterization of taint tracking
  as a form of lockstep-noninterference.
\item We introduce a novel stack safety property that allows for
  the notion of observability to change dynamically throughout
  execution.
\item We develop a testing framework for testing such
  lockstep-hyperproperties, implemented as a parametric co-processor
  for RISC-V.
\end{itemize}

@@

\begin{itemize}
\item Daniel's tainting paper (and some refs cited there)
      \cite{DBLP:conf/eurosp/SchoepeBPS16} 
\item Nick and Andre's papers (and other micropolicy papers)
\item StkTokens: Skorstengaard, Devriese, Birkedal
\begin{itemize}
\item {https://arxiv.org/pdf/1811.02787.pdf}
\item {https://arxiv.org/pdf/1902.05283.pdf}
\item {http://cs.au.dk/~lask/papers/esop2018.pdf}
\item {https://dl.acm.org/doi/fullHtml/10.1145/3363519}
\end{itemize}

\item Stuff about dynamically changing labels (see footnote in Testing
Noninterference Quickly paper)
